---
title: "bootstrap"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "C:/Users/slewa/Projects/heat_stress")

library(tidyverse)
library(readxl)
library(knitr)
library(kableExtra)
library(purrr)
library(furrr)
library(boot)
library(lme4)
library(ICC) 
library(dotwhisker)
library(broom)
library(car)
library(reshape2)
library(sjPlot)
library(readxl)
library(broom.mixed)
library(bbmle)
library(glmmTMB)
library(performance)
library(MASS)
library(mgcv)
library(gridExtra)
library(tableone)
library(corrr)
library(psych)
library(zoo)
library(patchwork) # install_github("thomasp85/patchwork")
```

Annual models from DMED data.

## Load and prepare data
```{r load_datasets, message = FALSE}

joined_hsi <-
  read_rds("data/joined_hsi.rds")

canopy_stats <-
  read_rds("data/canopy_stats_na_reclassified.rds") %>% 
  mutate(installation_lower = janitor::make_clean_names(installation))

# Remove Fort Irwin/NTC due to low counts/rates and transient training
# Remove initial year of health outcomes (1990 for Hospitilizations, 1997 for Ambulatory)

hsi_data <-
  joined_hsi %>% 
    left_join(canopy_stats %>% 
                dplyr::select(installation_lower, mean_canopy),
              by = c("installation" = "installation_lower")) %>% 
    filter(!installation %in% "ntc_and_fort_irwin",
           !(type %in% "Hospitalizations" & year %in% 1990),
           !(type %in% "Ambulatory Data" & year %in% 1997)) %>% 
    mutate(installation = factor(installation, ordered = FALSE),
         index = factor(index, ordered = FALSE),
         type = factor(type, ordered = FALSE),
         bct = factor(bct), 
         installation = relevel(installation, ref = "fort_bliss"))

levels(hsi_data$installation)

summary(hsi_data)


hsi_select <- hsi_data %>% 
  filter(index %in% c("days_tmp_gt85pct_may_sep",              #relative, heat season
                      "days_wbgt_gt85pct_may_sep",             #relative, heat season
                      "days_heat_index_gt85pct_may_sep",       #relative, heat season
                      "tmp_mean_may_sep",                      #absolute, heat season
                      "heat_index_mean_may_sep",               #absolute, heat season
                      "wbgt_f_mean_may_sep",                   #absolute, heat season
                      "tmp_f_mean",                            #absolute, year-round
                      "heat_index_mean",                       #absolute, year-round
                      "wbgt_f_mean"))                          #absolute, year-round


hsi_select

```

### Outcome-specific datasets

```{r outcome_filtered}

ambulatory_data <-
  hsi_select %>%
      filter(type %in% "Ambulatory Data") %>% 
      dplyr::select(index, installation, year, count, value, population) %>% 
      mutate(installation = as.character(installation))


hospitalization_data <-
  hsi_select %>%
      filter(type %in% "Hospitalizations") %>% 
      dplyr::select(index, installation, year, count, value, population) %>% 
      mutate(installation = as.character(installation))


rme_data <-
  hsi_select %>%
      filter(type %in% "Reportable Events") %>% 
      dplyr::select(index, installation, year, count, value, population) %>% 
      mutate(installation = as.character(installation))


ambulatory_data_full <-
  hsi_data %>%
      filter(type %in% "Ambulatory Data") %>% 
      dplyr::select(index, installation, year, count, value, population) %>% 
      mutate(installation = as.character(installation))


hospitalization_data_full <-
  hsi_data %>%
      filter(type %in% "Hospitalizations") %>% 
      dplyr::select(index, installation, year, count, value, population) %>% 
      mutate(installation = as.character(installation))


rme_data_full <-
  hsi_data %>%
      filter(type %in% "Reportable Events") %>% 
      dplyr::select(index, installation, year, count, value, population) %>% 
      mutate(installation = as.character(installation))



```



Note: "days_tmp_gt95pct_may_sep", for each calendar day, compares mean daily temperature with 95th %-ile of 30-year (1990-2019) climatology for that day


### Read-in bootstrap model data 

```{r read_in_models}

amb_boot_2yr_block <- read_rds("data/amb_boot_2yr_block.rds")
hosp_boot_2yr_block <- read_rds("data/hosp_boot_2yr_block.rds")
rme_boot_2yr_block <- read_rds("data/rme_boot_2yr_block.rds")

amb_boot_2yr_block_all <- read_rds("data/amb_boot_2yr_block_all.rds")
hosp_boot_2yr_block_all <- read_rds("data/hosp_boot_2yr_block_all.rds")
rme_boot_2yr_block_all <- read_rds("data/rme_boot_2yr_block_all.rds")


amb_boot_3yr_block <- read_rds("data/amb_boot_3yr_block.rds")
hosp_boot_3yr_block <- read_rds("data/hosp_boot_3yr_block.rds")
rme_boot_3yr_block <- read_rds("data/rme_boot_3yr_block.rds")

amb_boot_std <- read_rds("data/amb_boot_std.rds")
hosp_boot_std <- read_rds("data/hosp_boot_std.rds")
rme_boot_std <- read_rds("data/rme_boot_std.rds")

amb_nb <- read_rds("data/amb_nb.rds")
hosp_nb <- read_rds("data/hosp_nb.rds")
rme_nb <- read_rds("data/rme_nb.rds")
```





## Base models (with and without year)

```{r}

nb_fun = function(df) {
  df %>%
    MASS::glm.nb(count ~ value + installation + offset(log(population)), data = .)
}

nb_year_fun = function(df) {
  df %>%
    MASS::glm.nb(count ~ value + installation + year + offset(log(population)), data = .)
}


amb_nb <-
  ambulatory_data %>% 
    nest(data = installation:population) %>% 
    mutate(nb_mod = map(data, nb_fun),
           nb_tidy =   map(nb_mod, ~ broom::tidy(., conf.int = TRUE)),
           nb_year_mod = map(data, nb_year_fun),
           nb_year_tidy = map(nb_year_mod, ~ broom::tidy(., conf.int = TRUE)))


hosp_nb <-
  hospitalization_data %>% 
    nest(data = installation:population) %>% 
    mutate(nb_mod = map(data, nb_fun),
           nb_tidy =   map(nb_mod, ~ broom::tidy(., conf.int = TRUE)),
           nb_year_mod = map(data, nb_year_fun),
           nb_year_tidy = map(nb_year_mod, ~ broom::tidy(., conf.int = TRUE)))

hosp_nb 


rme_nb <-
  rme_data %>% 
    nest(data = installation:population) %>% 
    mutate(nb_mod = map(data, nb_fun),
           nb_tidy =   map(nb_mod, ~ broom::tidy(., conf.int = TRUE)),
           nb_year_mod = map(data, nb_year_fun),
           nb_year_tidy = map(nb_year_mod, ~ broom::tidy(., conf.int = TRUE)))


#write_rds(amb_nb, "data/amb_nb.rds")
#write_rds(hosp_nb, "data/hosp_nb.rds")
#write_rds(rme_nb, "data/rme_nb.rds")

```



## Bootstrap negative binomial models

Issue: control for long-term time trends; including `year` as a dummy time variable pulls variane also associated with changes in temperature/heat.

Approach: bootstrap model, selecting iterations of 2-3 year intervals to control for time trend.  
Execute resampling of dataset and calculation of your statistics on these samples.


## Random year blocks

### 2-year block limits (min and max year)
```{r random_blocks}

set.seed(82)

amb_min_yr <- min(as.numeric(
                hsi_select %>% 
                  filter(type %in% "Ambulatory Data") %>% 
                  pull(year)))

amb_max_yr <- max(as.numeric(
                hsi_select %>% 
                  filter(type %in% "Ambulatory Data") %>% 
                  pull(year)))


# Create randomized year dataframe (not currently used)
# Random years for two year block
amb_random_yrs_10k <- sample(amb_min_yr:(amb_max_yr - 1), size = 10000, replace = TRUE) 

# Dataframe of 10,000 random two year blocks
amb_two_yr_blocks <-
  amb_random_yrs_10k %>% 
    tibble::enframe(name = NULL) %>% 
    rename(first_yr = value) %>% 
    mutate(second_yr = first_yr + 1) 

amb_two_yr_blocks

################################################################

hosp_min_yr <- min(as.numeric(
                hsi_select %>% 
                  filter(type %in% "Hospitalizations") %>% 
                  pull(year)))

hosp_max_yr <- max(as.numeric(
                hsi_select %>% 
                  filter(type %in% "Hospitalizations") %>% 
                  pull(year)))



######################################################################

rme_min_yr <- min(as.numeric(
                hsi_select %>% 
                  filter(type %in% "Reportable Events") %>% 
                  pull(year)))

rme_max_yr <- max(as.numeric(
                hsi_select %>% 
                  filter(type %in% "Reportable Events") %>% 
                  pull(year)))

# For two year block

rme_random_yrs_10k <- sample(rme_min_yr:(rme_max_yr - 1), size = 10000, replace = TRUE) 

# Dataframe of 10,000 random two year blocks
rme_two_yr_blocks <-
  rme_random_yrs_10k %>% 
    tibble::enframe(name = NULL) %>% 
    rename(first_yr = value) %>% 
    mutate(second_yr = first_yr + 1) 

rme_two_yr_blocks

```


### Bootstrap random two year blocks
Draw random blocks with replacement; stitch to original dataframe length

```{r amb_boot_2yr, eval = FALSE}

amb_index_2yr_fun <- function(x, i) {
  # Select random start year
  random_year <- replicate(10, sample(amb_min_yr:(amb_max_yr - 1), size = 1, replace = TRUE))
  # select the observations to subset. 
  block_obs <- 
    map_dfr(random_year, ~ x %>% 
      filter(year %in% c(random_year, random_year + 1) ))
  # run regression for given replicate, return estimated coefficients
  coefficients(MASS::glm.nb(count ~ value + installation + offset(log(population)), data = block_obs))
}

# citation("MASS")

ptm <- proc.time()

amb_boot_2yr_block <-
  ambulatory_data %>% 
    nest(amb_data = installation:population) %>% 
  mutate(boot = map(amb_data, ~ boot(., amb_index_2yr_fun, 10000)),
         tidy = map(boot, ~ broom::tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "basic")))

proc.time() - ptm


amb_boot_2yr_block <-
  amb_boot_2yr_block %>% 
    mutate(tidy_bca = map(boot, ~ tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "bca")))

# Warnings: In norm.inter(t, adj.alpha) : extreme order statistics used as endpoints

#write_rds(amb_boot_2yr_block, path = "data/amb_boot_2yr_block.rds")


```


```{r hosp_boot_2yr, eval = FALSE}

hosp_index_2yr_fun <- function(x, i) {
  # Select random start year
  random_year <- replicate(13, sample(hosp_min_yr:(hosp_max_yr - 1), size = 1, replace = TRUE))
  # select the observations to subset. 
  block_obs <- 
    map_dfr(random_year, ~ x %>% 
      filter(year %in% c(random_year, random_year + 1) ))
  # run regression for given replicate, return estimated coefficients
  coefficients(MASS::glm.nb(count ~ value + installation + offset(log(population)), data = block_obs))
}


ptm <- proc.time()

hosp_boot_2yr_block <-
  hospitalization_data %>% 
    nest(hosp_data = installation:population) %>% 
  mutate(boot = map(hosp_data, ~ boot(., hosp_index_2yr_fun, 10000)),
         tidy = map(boot, ~ tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "basic")))

proc.time() - ptm

hosp_boot_2yr_block <-
  hosp_boot_2yr_block %>% 
    mutate(tidy_bca = map(boot, ~ tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "bca")))


# 41 warnings for BCa CI, In norm.inter(t, adj.alpha) : extreme order statistics used as endpoints


write_rds(hosp_boot_2yr_block, path = "data/hosp_boot_2yr_block.rds")

```

```{r  rme_boot_2yr, eval = FALSE}

rme_index_2yr_fun <- function(x, i) {
  # Select random start year
  random_year <- replicate(11, sample(rme_min_yr:(rme_max_yr - 1), size = 1, replace = TRUE))
  # select the observations to subset. 
  block_obs <- 
    map_dfr(random_year, ~ x %>% 
      filter(year %in% c(random_year, random_year + 1) ))
  # run regression for given replicate, return estimated coefficients
  coefficients(MASS::glm.nb(count ~ value + installation + offset(log(population)), data = block_obs))
}


ptm <- proc.time()

rme_boot_2yr_block <-
  rme_data %>% 
    nest(re_data = installation:population) %>% 
  mutate(boot = map(re_data, ~ boot(., rme_index_2yr_fun, 10000)),
         tidy = map(boot, ~ tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "basic")))

proc.time() - ptm

rme_boot_2yr_block <-
  rme_boot_2yr_block %>% 
    mutate(tidy_bca = map(boot, ~ tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "bca")))

# In norm.inter(t, adj.alpha) : extreme order statistics used as endpoints

#write_rds(rme_boot_2yr_block, path = "data/rme_boot_2yr_block.rds")



```


### All indices
RR whisker plot and table

```{r all_indices, eval = FALSE}
ptm <- proc.time()

amb_boot_2yr_block_all <-
  ambulatory_data_full %>% 
    nest(amb_data = installation:population) %>% 
  mutate(boot = map(amb_data, ~ boot(., amb_index_2yr_fun, 100)),
         tidy = map(boot, ~ broom::tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "basic")))

proc.time() - ptm

#write_rds(amb_boot_2yr_block_all, path = "data/amb_boot_2yr_block_all.rds")



 rme_boot_2yr_block_all %>% 
    unnest(tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(statistic))) %>% 
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Reportable Event Rate Ratios from Annual Indices of Heat") +
         xlab("Rate Ratio")
         


ggsave("rme_all.png", width = 8, height = 10.5)




## Combined panel RR plot


amb_boot2_long <-
  amb_boot_2yr_block_all %>%
    unnest(tidy) %>% 
    filter(term %in% "value") %>% 
    dplyr::select(index, statistic, conf.low, conf.high) %>% 
    pivot_longer(cols = -index,
                 names_to = "term",
                 values_to = "value") %>% 
    mutate(outcome = "Ambulatory")
  
  
hosp_boot2_long <-
  hosp_boot_2yr_block_all %>%
    unnest(tidy) %>% 
    filter(term %in% "value") %>% 
    dplyr::select(index, statistic, conf.low, conf.high) %>% 
    pivot_longer(cols = -index,
                 names_to = "term",
                 values_to = "value") %>% 
    mutate(outcome = "Hospitalizations")  


rme_boot2_long <-
  rme_boot_2yr_block_all %>%
    unnest(tidy) %>% 
    filter(term %in% "value") %>% 
    dplyr::select(index, statistic, conf.low, conf.high) %>% 
    pivot_longer(cols = -index,
                 names_to = "term",
                 values_to = "value") %>% 
    mutate(outcome = "Reportable Events")  


# Join dataframes

boot2_long <-
  amb_boot2_long %>% 
    bind_rows(hosp_boot2_long) %>% 
    bind_rows(rme_boot2_long)


## Full Index RR Plot - Facet
boot2_long %>% 
  pivot_wider(names_from = term, 
              values_from = value) %>%
  mutate(index = fct_reorder(index, exp(statistic))) %>% 
  ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         facet_wrap(~outcome) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
          ggtitle("HSI Rate Ratios from Annual Indices of Heat") +
         xlab("Rate Ratio")
  
  
## Reduced Index RR Plot - Facet
 # remove focus indices, sd, minimum temperatures 
  
   

boot2_long %>% 
  pivot_wider(names_from = term, 
              values_from = value) %>%
  filter(!index %in% c("tmp_f_mean", "wbgt_f_mean", "heat_index_mean",
                       "tmp_f_mean_may_sep", "wbgt_f_mean_may_sep", "heat_index_mean_may_sep",
                       "tmp_f_sd", "wbgt_f_sd", "heat_index_sd",
                       "tmp_f_min", "heat_index_min", "wbgt_f_min")) %>% 
  mutate(index = fct_reorder(index, exp(statistic))) %>% 
  ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         facet_wrap(~outcome) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
          ggtitle("HSI Rate Ratios from Annual Indices of Heat") +
         xlab("Rate Ratio")


ggsave("boot2_reduced.png", width = 7.5, height = 9)





# Divide by degree units and days/hours

# Modify units: multiply hours by 24

# Degree indices
boot2_long %>% 
  pivot_wider(names_from = term, 
              values_from = value) %>%
  filter(!index %in% c("tmp_f_mean", "wbgt_f_mean", "heat_index_mean",
                       "tmp_f_mean_may_sep", "wbgt_f_mean_may_sep", "heat_index_mean_may_sep",
                       "tmp_f_sd", "wbgt_f_sd", "heat_index_sd",
                       "tmp_f_min", "heat_index_min", "wbgt_f_min"),
         !str_detect(index, "hour"),
         !str_detect(index, "day")) %>% 
  mutate(index = fct_reorder(index, exp(statistic))) %>% 
  ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         facet_wrap(~outcome) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
          #ggtitle("HSI Rate Ratios from Annual Indices of Heat") +
         xlab("Rate Ratio")

ggsave("boot2_degrees.png", width = 8, height = 5)

# Days/hour indices


boot2_long %>%
  mutate(value = case_when(str_detect(index, "hour")  ~ value * 24,
                        TRUE ~ value)) %>% 
  pivot_wider(names_from = term, 
              values_from = value) %>%
  filter(!index %in% c("tmp_f_mean", "wbgt_f_mean", "heat_index_mean",
                       "tmp_f_mean_may_sep", "wbgt_f_mean_may_sep", "heat_index_mean_may_sep",
                       "tmp_f_sd", "wbgt_f_sd", "heat_index_sd",
                       "tmp_f_min", "heat_index_min", "wbgt_f_min"),
                        str_detect(index, "hour|day")) %>% 
  mutate(index = fct_reorder(index, exp(statistic))) %>% 
  ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         facet_wrap(~outcome) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
          #ggtitle("HSI Rate Ratios from Annual Indices of Heat") +
         xlab("Rate Ratio")


ggsave("boot2_days.png", width = 8, height = 5)


# Slice top 20 ambulatory statistic

# vector of top 20 ambulatory indices
amb_top20_boot2_days <-
  boot2_long %>%
    mutate(value = case_when(str_detect(index, "hour")  ~ value * 24,
                          TRUE ~ value)) %>% 
    pivot_wider(names_from = term, 
                values_from = value) %>%
    filter(!index %in% c("tmp_f_mean", "wbgt_f_mean", "heat_index_mean",
                         "tmp_f_mean_may_sep", "wbgt_f_mean_may_sep", "heat_index_mean_may_sep",
                         "tmp_f_sd", "wbgt_f_sd", "heat_index_sd",
                         "tmp_f_min", "heat_index_min", "wbgt_f_min"),
                          str_detect(index, "hour|day"),
           outcome %in% "Ambulatory") %>% 
    dplyr::arrange(desc(statistic)) %>% 
    dplyr::slice(1:20) %>% 
    dplyr::select(index)


boot2_long %>%
  mutate(value = case_when(str_detect(index, "hour")  ~ value * 24,
                        TRUE ~ value)) %>% 
  pivot_wider(names_from = term, 
              values_from = value) %>%
  dplyr::semi_join(amb_top20_boot2_days, by = "index") %>% 
  mutate(index = fct_reorder(index, exp(statistic))) %>% 
  ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         facet_wrap(~outcome) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
          #ggtitle("HSI Rate Ratios from Annual Indices of Heat") +
         xlab("Rate Ratio")


ggsave("boot2_days.png", width = 8, height = 5)





boot2_long %>% 
  mutate(value = case_when(str_detect(index, "hour")  ~ value * 24,
                        TRUE ~ value)) %>% 
  pivot_wider(names_from = term, 
              values_from = value) %>%
  filter(!index %in% c("tmp_f_mean", "wbgt_f_mean", "heat_index_mean",
                       "tmp_f_sd", "wbgt_f_sd", "heat_index_sd",
                       "tmp_f_min", "heat_index_min", "wbgt_f_min")) %>% 
  mutate(index = fct_reorder(index, exp(statistic))) %>% 
  ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         facet_wrap(~outcome) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
          ggtitle("HSI Rate Ratios from Annual Indices of Heat") +
         xlab("Rate Ratio")








# RR Table
amb_boot_2yr_block_all %>% 
  unnest(tidy) %>%
      filter(term %in% "value") %>% 
  dplyr::select(index, statistic, bias, conf.low, conf.high) %>% 
  mutate(rr = exp(statistic),
         rr_low = exp(conf.low),
         rr_high = exp(conf.high),
         rate_ratio = paste0(round(rr, 2), " (", round(rr_low, 2), ", ", round(rr_high, 2), ")")) %>% 
  dplyr::select(index, rate_ratio) %>% 
  as.data.frame() %>% print()


```

# Sensitivity analysis plots



```{r}

a1 <-
amb_boot_2yr_block %>% 
    unnest(tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(statistic))) %>% 
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Ambulatory \n 2 year block (primary analysis, 10k)") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))

a2 <-
amb_boot_2yr_block %>% 
    unnest(tidy_bca) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(statistic))) %>% 
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Ambulatory \n 2 year block - Bca CIs, 10k") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))

a3 <-
amb_boot_3yr_block %>% 
    unnest(tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(statistic))) %>% 
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Ambulatory \n 3 year block, 10k") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))


a4 <-
amb_boot_std %>% 
    unnest(tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(statistic))) %>% 
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Ambulatory \n standard bootstrap (single year, 10k)") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))

a5 <-
amb_nb %>% 
    unnest(nb_tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(estimate))) %>% 
   ggplot() +
        geom_point(aes(x = exp(estimate), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Ambulatory \n neg bin - no year term, no bootstrap") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))

a6 <-
amb_nb %>% 
    unnest(nb_year_tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(estimate))) %>% 
   ggplot() +
        geom_point(aes(x = exp(estimate), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Ambulatory \n neg bin - with year term, no bootstrap") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))


#patchwork
(a1 + a2 + a3) / (a4 + a5 + a6)

ggsave("amb_sens.png", width = 10, height = 6)
```



```{r}

r1 <-
rme_boot_2yr_block %>% 
    unnest(tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(statistic))) %>% 
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Reportable Events \n 2 year block (primary analysis, 10k)") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))

r2 <-
rme_boot_2yr_block %>% 
    unnest(tidy_bca) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(statistic))) %>% 
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Reportable Events \n 2 year block - Bca CIs, 10k") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))

r3 <-
rme_boot_3yr_block %>% 
    unnest(tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(statistic))) %>% 
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Reportable Events \n 3 year block, 10k") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))


r4 <-
rme_boot_std %>% 
    unnest(tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(statistic))) %>% 
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Reportable Events \n standard bootstrap (single year, 10k)") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))

r5 <-
rme_nb %>% 
    unnest(nb_tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(estimate))) %>% 
   ggplot() +
        geom_point(aes(x = exp(estimate), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Reportable Events \n neg bin - no year term, no bootstrap") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))

r6 <-
rme_nb %>% 
    unnest(nb_year_tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(estimate))) %>% 
   ggplot() +
        geom_point(aes(x = exp(estimate), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Reportable Events \n neg bin - with year term, no bootstrap") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))


#patchwork
(r1 + r2 + r3) / (r4 + r5 + r6)

ggsave("rme_sens.png", width = 10, height = 6)
```






### Hospitalization, all indices, 100 bootstrap

```{r}
ptm <- proc.time()

hosp_boot_2yr_block_all <-
  hospitalization_data_full %>% 
    nest(hosp_data = installation:population) %>% 
  mutate(boot = map(hosp_data, ~ boot(., hosp_index_2yr_fun, 100)),
         tidy = map(boot, ~ broom::tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "basic")))

proc.time() - ptm

#write_rds(hosp_boot_2yr_block_all, path = "data/hosp_boot_2yr_block_all.rds")



hosp_boot_2yr_block_all %>% 
  unnest(tidy) %>%
      filter(term %in% "value") %>%
 ggplot() +
      geom_point(aes(x = exp(statistic), y = index)) +
      geom_point(aes(x = exp(statistic + bias), y = index), color = "red", shape = 4) +
      geom_errorbarh(
        aes(y = index,
            xmin = exp(conf.low),
            xmax = exp(conf.high))) +
       geom_vline(aes(xintercept = 1), colour = "blue") +
       theme_bw() +
       theme(axis.text.y = element_text(size = rel(0.75))) +
       ggtitle("Hospitalization Rate Ratio, Bootstrap, 2 year block, 100 iterations")


hosp_boot_2yr_block_all %>% 
  unnest(tidy) %>%
      filter(term %in% "value") %>% 
  dplyr::select(index, statistic, bias, conf.low, conf.high) %>% 
  mutate(rr = exp(statistic),
         rr_low = exp(conf.low),
         rr_high = exp(conf.high),
         rate_ratio = paste0(round(rr, 2), " (", round(rr_low, 2), ", ", round(rr_high, 2), ")")) %>% 
  dplyr::select(index, rate_ratio) %>% 
  as.data.frame() %>% print()
```



```{r}


ptm <- proc.time()

rme_boot_2yr_block_all <-
  rme_data_full %>% 
    nest(rme_data = installation:population) %>% 
  mutate(boot = map(rme_data, ~ boot(., rme_index_2yr_fun, 100)),
         tidy = map(boot, ~ broom::tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "basic")))

proc.time() - ptm

#write_rds(rme_boot_2yr_block_all, path = "data/rme_boot_2yr_block_all.rds")


rme_boot2_all_plot <-
  rme_boot_2yr_block_all %>% 
    unnest(tidy) %>%
        filter(term %in% "value") %>%
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_point(aes(x = exp(statistic + bias), y = index), color = "red", shape = 4) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75))) +
         ggtitle("Reportable Event Rate Ratio, Bootstrap, 2 year block, 100 iterations")

# Limit x axis (RR) to 2.5
  rme_boot_2yr_block_all %>% 
    unnest(tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(statistic))) %>% 
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Reportable Events") +
         xlab("Rate Ratio")
         


#ggsave("rme_all.png", width = 8, height = 10.5)


rme_boot_2yr_block_all %>% 
  unnest(tidy) %>%
      filter(term %in% "value") %>% 
  dplyr::select(index, statistic, bias, conf.low, conf.high) %>% 
  mutate(rr = exp(statistic),
         rr_low = exp(conf.low),
         rr_high = exp(conf.high),
         rate_ratio = paste0(round(rr, 2), " (", round(rr_low, 2), ", ", round(rr_high, 2), ")")) %>% 
  dplyr::select(index, rate_ratio) %>% 
  as.data.frame() %>% print()
```



### Bootstrap 2 year block plots

```{r}
amb_boot_2yr_block %>% 
  unnest(tidy) %>%
      filter(term %in% "value") %>%
 ggplot() +
      geom_point(aes(x = exp(statistic), y = index)) +
      geom_point(aes(x = exp(statistic + bias), y = index), color = "red", shape = 4) +
      geom_errorbarh(
        aes(y = index,
            xmin = exp(conf.low),
            xmax = exp(conf.high))) +
       geom_vline(aes(xintercept = 1), colour = "blue") +
       theme_bw() +
       theme(axis.text.y = element_text(size = rel(0.75))) +
       ggtitle("Ambulatory Rate Ratio, Bootstrap, 2 year block, 10,000 iterations")


hosp_boot_2yr_block %>% 
  unnest(tidy) %>%
      filter(term %in% "value") %>%
 ggplot() +
      geom_point(aes(x = exp(statistic), y = index)) +
      geom_point(aes(x = exp(statistic + bias), y = index), color = "red", shape = 4) +
      geom_errorbarh(
        aes(y = index,
            xmin = exp(conf.low),
            xmax = exp(conf.high))) +
       geom_vline(aes(xintercept = 1), colour = "blue") +
       theme_bw() +
       theme(axis.text.y = element_text(size = rel(0.75))) +
       ggtitle("Hospitalization Rate Ratio, Bootstrap, 2 year block, 10,000 iterations")

rme_boot_2yr_block %>% 
  unnest(tidy) %>%
      filter(term %in% "value") %>%
 ggplot() +
      geom_point(aes(x = exp(statistic), y = index)) +
      geom_point(aes(x = exp(statistic + bias), y = index), color = "red", shape = 4) +
      geom_errorbarh(
        aes(y = index,
            xmin = exp(conf.low),
            xmax = exp(conf.high))) +
       geom_vline(aes(xintercept = 1), colour = "blue") +
       theme_bw() +
       theme(axis.text.y = element_text(size = rel(0.75))) +
       ggtitle("Reportable Event Rate Ratio, Bootstrap, 2 year block, 10,000 iterations")

```







## Bootstrap 3 year blocks


```{r amb_boot_3yr, eval = FALSE}

# 20 year timeframe (1998-2018: stitch 6 replicates of 3 year blocks

amb_index_3yr_fun <- function(x, i) {
  # Select random start year
  random_year <- replicate(6, sample(amb_min_yr:(amb_max_yr - 2), size = 1, replace = TRUE))
  # select the observations to subset. 
  block_obs <- 
    map_dfr(random_year, ~ x %>% 
      filter(year %in% c(random_year, random_year + 1, random_year + 2) ))
  # run regression for given replicate, return estimated coefficients
  coefficients(MASS::glm.nb(count ~ value + installation + offset(log(population)), data = block_obs))
}


ptm <- proc.time()

plan(multiprocess)

amb_boot_3yr_block <-
  ambulatory_data %>% 
    nest(amb_data = installation:population) %>% 
  mutate(boot = future_map(amb_data, ~ boot(., amb_index_3yr_fun, 10000)),
         tidy = future_map(boot, ~ tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "basic")))

proc.time() - ptm

write_rds(amb_boot_3yr_block, path = "data/amb_boot_3yr_block.rds")

```



```{r hosp_boot_3yr, eval = FALSE}

hosp_index_3yr_fun <- function(x, i) {
  # Select random start year
  random_year <- replicate(9, sample(hosp_min_yr:(hosp_max_yr - 2), size = 1, replace = TRUE))
  # select the observations to subset. 
  block_obs <- 
    map_dfr(random_year, ~ x %>% 
      filter(year %in% c(random_year, random_year + 1, random_year + 2) ))
  # run regression for given replicate, return estimated coefficients
  coefficients(MASS::glm.nb(count ~ value + installation + offset(log(population)), data = block_obs))
}


ptm <- proc.time()

hosp_boot_3yr_block <-
  hospitalization_data %>% 
    nest(hosp_data = installation:population) %>% 
  mutate(boot = future_map(hosp_data, ~ boot(., hosp_index_3yr_fun, 10000)))

proc.time() - ptm






write_rds(hosp_boot_3yr_block, path = "data/hosp_boot_3yr_block.rds")

hosp_boot_3yr_block <-
  hosp_boot_3yr_block %>% 
    mutate(tidy = map(boot, ~ tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "basic")),
           tidy_bca = map(boot, ~ tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "bca")))

# BCa CI warnings (34):  In norm.inter(t, adj.alpha) : extreme order statistics used as endpoints

```

```{r  rme_boot_3yr, eval = FALSE}

rme_index_3yr_fun <- function(x, i) {
  # Select random start year
  random_year <- replicate(7, sample(rme_min_yr:(rme_max_yr - 2), size = 1, replace = TRUE))
  # select the observations to subset. 
  block_obs <- 
    map_dfr(random_year, ~ x %>% 
      filter(year %in% c(random_year, random_year + 1, random_year + 2) ))
  # run regression for given replicate, return estimated coefficients
  coefficients(MASS::glm.nb(count ~ value + installation + offset(log(population)), data = block_obs))
}


ptm <- proc.time()

rme_boot_3yr_block <-
  rme_data %>% 
    nest(re_data = installation:population) %>% 
  mutate(boot = future_map(re_data, ~ boot(., rme_index_3yr_fun, 10000)))

rme_boot_3yr_block <-
  rme_boot_3yr_block %>% 
    mutate(tidy = map(boot, ~ tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "basic")))

proc.time() - ptm

write_rds(rme_boot_3yr_block, path = "data/rme_boot_3yr_block.rds")



```


## Bootstrap - original (draw single observations)

```{r boot_single, eval = FALSE}

std_boot <- function(D, d){
	E = D[d,]
	return(coefficients(MASS::glm.nb(count ~ value + installation + offset(log(population)), data = E)))
	
}

amb_boot_std <-
  ambulatory_data %>%
    nest(amb_data = installation:population) %>% 
    mutate(std_boot = map(amb_data, ~ boot(., std_boot, R = 10000)),          tidy = map(std_boot, ~ tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "basic")))


hosp_boot_std <-
  hospitalization_data %>%
    nest(hosp_data = installation:population) %>% 
    mutate(hosp_boot = map(hosp_data, ~ boot(., std_boot, R = 10000)))

hosp_boot_std <-
  hosp_boot_std %>%            
    mutate(tidy = map(hosp_boot, ~ tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "basic")))


rme_boot_std <-
  rme_data %>%
    nest(re_data = installation:population) %>% 
    mutate(rme_boot = map(re_data, ~ boot(., std_boot, R = 10000)))

rme_boot_std <-
  rme_boot_std %>%            
    mutate(tidy = map(rme_boot, ~ tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "basic")))


#write_rds(amb_boot_std, path = "data/amb_boot_std.rds")
#write_rds(hosp_boot_std, path = "data/hosp_boot_std.rds")
#write_rds(rme_boot_std, path = "data/rme_boot_std.rds")

```





### Bootstrap 3 year block plots

```{r}
amb_boot_3yr_block %>% 
  unnest(tidy) %>%
      filter(term %in% "value") %>%
 ggplot() +
      geom_point(aes(x = exp(statistic), y = index)) +
      geom_point(aes(x = exp(statistic + bias), y = index), color = "red", shape = 4) +
      geom_errorbarh(
        aes(y = index,
            xmin = exp(conf.low),
            xmax = exp(conf.high))) +
       geom_vline(aes(xintercept = 1), colour = "blue") +
       theme_bw() +
       theme(axis.text.y = element_text(size = rel(0.75))) +
       ggtitle("Ambulatory Rate Ratio, Bootstrap, 3 year block, 10,000 iterations")


hosp_boot_3yr_block %>% 
  unnest(tidy) %>%
      filter(term %in% "value") %>%
 ggplot() +
      geom_point(aes(x = exp(statistic), y = index)) +
      geom_point(aes(x = exp(statistic + bias), y = index), color = "red", shape = 4) +
      geom_errorbarh(
        aes(y = index,
            xmin = exp(conf.low),
            xmax = exp(conf.high))) +
       geom_vline(aes(xintercept = 1), colour = "blue") +
       theme_bw() +
       theme(axis.text.y = element_text(size = rel(0.75))) +
       ggtitle("Hospitalization Rate Ratio, Bootstrap, 3 year block, 10,000 iterations")






rme_boot_3yr_block %>% 
  unnest(tidy) %>%
      filter(term %in% "value") %>%
 ggplot() +
      geom_point(aes(x = exp(statistic), y = index)) +
      geom_point(aes(x = exp(statistic + bias), y = index), color = "red", shape = 4) +
      geom_errorbarh(
        aes(y = index,
            xmin = exp(conf.low),
            xmax = exp(conf.high))) +
       geom_vline(aes(xintercept = 1), colour = "blue") +
       theme_bw() +
       theme(axis.text.y = element_text(size = rel(0.75))) +
       ggtitle("Reportable Event Rate Ratio, Bootstrap, 3 year block, 10,000 iterations")

```

### Bootstrap 2 year block plots - BCa CI

```{r two_yr_bca, eval = FALSE}

# Hosp with BCa CI
hosp_boot_2yr_block %>% 
  unnest(tidy_bca) %>%
    filter(term %in% "value") %>%
 ggplot() +
      geom_point(aes(x = exp(statistic), y = index)) +
      geom_point(aes(x = exp(statistic + bias), y = index), color = "red", shape = 4) +
      geom_errorbarh(
        aes(y = index,
            xmin = exp(conf.low),
            xmax = exp(conf.high))) +
       geom_vline(aes(xintercept = 1), color = "blue") +
       theme_bw() +
       theme(axis.text.y = element_text(size = rel(0.75))) +
       ggtitle("Hospitalization Rate Ratio, Bootstrap, 2 year block, 10,000 iterations")



hosp_boot_2yr_block %>% 
  unnest(tidy_bca) %>%
    filter(term %in% "value") %>%
 ggplot() +
      geom_point(aes(x = exp(statistic), y = index)) +
      geom_point(aes(x = exp(statistic + bias), y = index), color = "red", shape = 4) +
      geom_errorbarh(
        aes(y = index,
            xmin = exp(conf.low),
            xmax = exp(conf.high))) +
       geom_vline(aes(xintercept = 1), color = "blue") +
       theme_bw() +
       theme(axis.text.y = element_text(size = rel(0.75))) +
       ggtitle("Hospitalization Rate Ratio, Bootstrap, 2 year block, 10,000 iterations")



rme_boot_2yr_block %>% 
  unnest(tidy_bca) %>%
      filter(term %in% "value") %>%
 ggplot() +
      geom_point(aes(x = exp(statistic), y = index)) +
      geom_point(aes(x = exp(statistic + bias), y = index), color = "red", shape = 4) +
      geom_errorbarh(
        aes(y = index,
            xmin = exp(conf.low),
            xmax = exp(conf.high))) +
       geom_vline(aes(xintercept = 1), colour = "blue") +
       theme_bw() +
       theme(axis.text.y = element_text(size = rel(0.75))) +
       ggtitle("Reportable Event Rate Ratio, Bootstrap, 2 year block, 10,000 iterations")

```




## Grouped CI plots

```{r}


amb_grouped <-
  amb_nb %>% 
    unnest(nb_tidy) %>%
      filter(term %in% "value") %>% 
    dplyr::select(index, estimate, conf.low, conf.high) %>%
    mutate(model = "nb_no_yr",
           bias = as.numeric("NA")) %>%
    rename(statistic = estimate) %>% 
  bind_rows(
    amb_nb %>% 
      unnest(nb_year_tidy) %>%
        filter(term %in% "value") %>% 
    dplyr::select(index, estimate, conf.low, conf.high) %>%
    mutate(model = "nb_yr",
           bias = as.numeric("NA")) %>%
    rename(statistic = estimate)
    ) %>%
    bind_rows(  
    amb_boot_std %>% 
        unnest(tidy) %>%
          filter(term %in% "value") %>% 
          mutate(model = "boot") %>% 
      dplyr::select(index, statistic, bias, conf.low, conf.high, model)
    ) %>% 
  bind_rows(  
    amb_boot_2yr_block %>% 
      unnest(tidy) %>%
        filter(term %in% "value") %>% 
        mutate(model = "boot2yr_basic") %>% 
    dplyr::select(index, statistic, bias, conf.low, conf.high, model)
    ) %>% 
  bind_rows(
   amb_boot_3yr_block %>% 
    unnest(tidy) %>%
      filter(term %in% "value") %>% 
      mutate(model = "boot3yr_basic") %>% 
  dplyr::select(index, statistic, bias, conf.low, conf.high, model)

)



hosp_grouped <-
  hosp_nb %>% 
    unnest(nb_tidy) %>%
      filter(term %in% "value") %>% 
    dplyr::select(index, estimate, conf.low, conf.high) %>%
    mutate(model = "nb_no_yr",
           bias = as.numeric("NA")) %>%
    rename(statistic = estimate) %>% 
  bind_rows(
    hosp_nb %>% 
      unnest(nb_year_tidy) %>%
        filter(term %in% "value") %>% 
    dplyr::select(index, estimate, conf.low, conf.high) %>%
    mutate(model = "nb_yr",
           bias = as.numeric("NA")) %>%
    rename(statistic = estimate)
    ) %>%
    bind_rows(  
    hosp_boot_std %>% 
        unnest(tidy) %>%
          filter(term %in% "value") %>% 
          mutate(model = "boot") %>% 
      dplyr::select(index, statistic, bias, conf.low, conf.high, model)
    ) %>% 
  bind_rows(  
    hosp_boot_2yr_block %>% 
      unnest(tidy) %>%
        filter(term %in% "value") %>% 
        mutate(model = "boot2yr_basic") %>% 
    dplyr::select(index, statistic, bias, conf.low, conf.high, model)
    ) %>% 
  bind_rows(
    hosp_boot_2yr_block %>% 
    unnest(tidy_bca) %>%
      filter(term %in% "value") %>% 
      mutate(model = "boot2yr_bca") %>% 
  dplyr::select(index, statistic, bias, conf.low, conf.high, model)
) %>% 
  bind_rows(
   hosp_boot_3yr_block %>% 
    unnest(tidy) %>%
      filter(term %in% "value") %>% 
      mutate(model = "boot3yr_basic") %>% 
  dplyr::select(index, statistic, bias, conf.low, conf.high, model)
  ) %>% 
  bind_rows(
    hosp_boot_3yr_block %>% 
    unnest(tidy_bca) %>%
      filter(term %in% "value") %>% 
      mutate(model = "boot3yr_bca") %>% 
  dplyr::select(index, statistic, bias, conf.low, conf.high, model)
)




rme_grouped <-
  rme_nb %>% 
    unnest(nb_tidy) %>%
      filter(term %in% "value") %>% 
    dplyr::select(index, estimate, conf.low, conf.high) %>%
    mutate(model = "nb_no_yr",
           bias = as.numeric("NA")) %>%
    rename(statistic = estimate) %>% 
  bind_rows(
    rme_nb %>% 
      unnest(nb_year_tidy) %>%
        filter(term %in% "value") %>% 
    dplyr::select(index, estimate, conf.low, conf.high) %>%
    mutate(model = "nb_yr",
           bias = as.numeric("NA")) %>%
    rename(statistic = estimate)
    ) %>%
    bind_rows(  
    rme_boot_std %>% 
        unnest(tidy) %>%
          filter(term %in% "value") %>% 
          mutate(model = "boot") %>% 
      dplyr::select(index, statistic, bias, conf.low, conf.high, model)
    ) %>% 
  bind_rows(  
    rme_boot_2yr_block %>% 
      unnest(tidy) %>%
        filter(term %in% "value") %>% 
        mutate(model = "boot2yr_basic") %>% 
    dplyr::select(index, statistic, bias, conf.low, conf.high, model)
    ) %>% 
  bind_rows(
   rme_boot_3yr_block %>% 
    unnest(tidy) %>%
      filter(term %in% "value") %>% 
      mutate(model = "boot3yr_basic") %>% 
  dplyr::select(index, statistic, bias, conf.low, conf.high, model)
)



# Plot
# 

amb_grouped %>%
#filter(!model %in% c("nb_no_yr", "boot2yr_bca", "boot3yr_bca")) %>% 
  ggplot(aes(fill = model, x = index)) +
        geom_point(aes(y = exp(statistic)), position = position_dodge(0.5)) +
        geom_point(aes(y = exp(statistic + bias)), shape = 4, position = position_dodge(0.5)) +
        geom_errorbar(
          aes(ymin = exp(conf.low),
              ymax = exp(conf.high),
          color = model),
              position = position_dodge(0.5)) +
         coord_flip() +
         geom_hline(aes(yintercept = 1), color = "blue") +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75))) +
         ggtitle("Ambulatory Rate Ratios")





hosp_grouped %>%
#filter(!model %in% c("nb_no_yr", "boot2yr_bca", "boot3yr_bca")) %>% 
  ggplot(aes(fill = model, x = index)) +
        geom_point(aes(y = exp(statistic)), position = position_dodge(0.5)) +
        geom_point(aes(y = exp(statistic + bias)), shape = 4, position = position_dodge(0.5)) +
        geom_errorbar(
          aes(ymin = exp(conf.low),
              ymax = exp(conf.high),
          color = model),
              position = position_dodge(0.5)) +
         coord_flip() +
         geom_hline(aes(yintercept = 1), color = "blue") +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75))) +
         ggtitle("Hospitalization Rate Ratios")

rme_grouped %>% 
#filter(!model %in% c("nb_no_yr", "boot2yr_bca", "boot3yr_bca")) %>% 
  ggplot(aes(fill = model, x = index)) +
        geom_point(aes(y = exp(statistic)), position = position_dodge(0.5)) +
        geom_point(aes(y = exp(statistic + bias)), shape = 4, position = position_dodge(0.5)) +
        geom_errorbar(
          aes(ymin = exp(conf.low),
              ymax = exp(conf.high),
          color = model),
              position = position_dodge(0.5)) +
         coord_flip() +
         geom_hline(aes(yintercept = 1), color = "blue") +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75))) +
         ggtitle("Reportable Event Rate Ratios")



```



## Select Plots

```{r}
rme_grouped %>% 
  filter(!model %in% c("boot3yr_basic", "boot2yr_bca", "boot3yr_bca"),
         index %in% c("tmp_mean_may_sep", "heat_index_mean_may_sep", "wbgt_f_mean_may_sep")) %>% 
    ggplot(aes(fill = model, x = index)) +
          geom_point(aes(y = exp(statistic)), position = position_dodge(0.75)) +
          geom_point(aes(y = exp(statistic + bias)), shape = 4, position = position_dodge(0.75)) +
          geom_errorbar(
            aes(ymin = exp(conf.low),
                ymax = exp(conf.high),
            color = model),
                position = position_dodge(0.75)) +
           coord_flip() +
           geom_hline(aes(yintercept = 1), color = "blue") +
           theme_bw() +
           theme(axis.text.y = element_text(size = rel(0.75))) +
           ggtitle("Reportable Event Rate Ratios")



# wbgt, RME 2 yr block boot histogram
plot(rme_boot_2yr_block[6,3][[1]][[1]], index = 2)



as.data.frame(rme_boot_2yr_block[6,3][[1]][[1]]$t)


## RR, May-Sep temp, 2 yr boot histogram
ggplot() + 
  geom_histogram(data = exp(as.data.frame(rme_boot_2yr_block[4,3][[1]][[1]]$t)), aes(V2), bins = 200) +
  geom_vline(xintercept = exp(rme_boot_2yr_block[4,4][[1]][[1]][2,5] %>% pull()), color = "blue") +
  geom_vline(xintercept = exp(rme_boot_2yr_block[4,4][[1]][[1]][2,6] %>% pull()), color = "blue") +
  ggtitle("Reportable Events, Warm-Season Temp (deg F) \n 2 year block bootstrap") +
  xlab("Risk Ratio") +
  theme_bw()

## RR, May-Sep HI, 2 yr boot histogram
ggplot() + 
  geom_histogram(data = exp(as.data.frame(rme_boot_2yr_block[5,3][[1]][[1]]$t)), aes(V2), bins = 200) +
  geom_vline(xintercept = exp(rme_boot_2yr_block[5,4][[1]][[1]][2,5] %>% pull()), color = "blue") +
  geom_vline(xintercept = exp(rme_boot_2yr_block[5,4][[1]][[1]][2,6] %>% pull()), color = "blue") +
  ggtitle("Reportable Events, Warm-Season HI (deg F) \n 2 year block bootstrap") +
  xlab("Risk Ratio") +
  theme_bw()

## RR, May-Sep WBGT, 2 yr boot histogram
ggplot() + 
  geom_histogram(data = exp(as.data.frame(rme_boot_2yr_block[6,3][[1]][[1]]$t)), aes(V2), bins = 200) +
  geom_vline(xintercept = exp(rme_boot_2yr_block[6,4][[1]][[1]][2,5] %>% pull()), color = "blue") +
  geom_vline(xintercept = exp(rme_boot_2yr_block[6,4][[1]][[1]][2,6] %>% pull()), color = "blue") +
  ggtitle("Reportable Events, Warm-Season WBGT \n 2 year block bootstrap") +
  xlab("Risk Ratio") +
  theme_bw()
  
  

```


### Bca CI histograms
```{r}

## RR, May-Sep temp, 2 yr boot histogram
ggplot() + 
  geom_histogram(data = exp(as.data.frame(hosp_boot_2yr_block[4,3][[1]][[1]]$t)), aes(V2), bins = 200) +
  geom_vline(xintercept = exp(hosp_boot_2yr_block[4,5][[1]][[1]][2,5] %>% pull()), color = "blue") +
  geom_vline(xintercept = exp(hosp_boot_2yr_block[4,5][[1]][[1]][2,6] %>% pull()), color = "blue") +
  ggtitle("Hospitalization, Warm-Season Temp (deg F) \n 2 year block bootstrap, Bca CI") +
  xlab("Risk Ratio") +
  theme_bw()


ggplot() + 
  geom_histogram(data = exp(as.data.frame(hosp_boot_2yr_block[4,3][[1]][[1]]$t)), aes(V2), bins = 200) +
  geom_vline(xintercept = exp(hosp_boot_2yr_block[4,4][[1]][[1]][2,5] %>% pull()), color = "blue") +
  geom_vline(xintercept = exp(hosp_boot_2yr_block[4,4][[1]][[1]][2,6] %>% pull()), color = "blue") +
  geom_vline(xintercept = exp(hosp_boot_2yr_block[4,4][[1]][[1]][2,2] %>% pull())) +
  geom_vline(xintercept = exp(
    (hosp_boot_2yr_block[4,4][[1]][[1]][2,2] %>% pull()) +
      hosp_boot_2yr_block[4,4][[1]][[1]][2,3] %>% pull()), linetype = "dashed") +
  ggtitle("Hospitalization, Warm-Season Temp (deg F) \n 2 year block bootstrap, Basic/Empirical CI") +
  xlab("Risk Ratio") +
  theme_bw()

```


# Autocorrelations
```{r}

# ACF of mean count per year across selected installations
# Ambulatory ACF
ambulatory_data %>%
  group_by(year) %>%
  summarise(mean_count = mean(count)) %>%
  pull(mean_count) %>% 
  acf()

# Hospitalization ACF
hospitalization_data %>%
  group_by(year) %>%
  summarise(mean_count = mean(count)) %>%
  pull(mean_count) %>% 
  acf()

# Reportable Events ACF
rme_data %>%
  group_by(year) %>%
  summarise(mean_count = mean(count)) %>%
  pull(mean_count) %>% 
  acf()
```


## Model Output Tables

```{r}
# RME model table - full year

rme_boot_2yr_block %>% 
  unnest(tidy) %>%
      filter(!str_detect(index, "days"),
             !str_detect(index, "may")) %>%
  mutate(coefficient = paste0(round(exp(statistic), 2)," ", "(", 
                              round(exp(conf.low), 2), ", ",
                              round(exp(conf.high), 2),
                              ")")) %>% 
  dplyr::select(index, term, coefficient) %>% 
  pivot_wider(names_from = index  , values_from = coefficient)
  








# RME model table - heat season

rme_boot_2yr_block %>% 
  unnest(tidy) %>%
      filter(!str_detect(index, "days"),
             str_detect(index, "may")) %>%
  mutate(coefficient = paste0(round(exp(statistic), 2)," ", "(", 
                              round(exp(conf.low), 2), ", ",
                              round(exp(conf.high), 2),
                              ")")) %>% 
  dplyr::select(index, term, coefficient) %>% 
  pivot_wider(names_from = index  , values_from = coefficient)

```

## Plots for Manuscript

```{r}


# Full Year

full_yr_df <-
   amb_boot_2yr_block %>% 
    unnest(tidy) %>%
    mutate(type = "Ambulatory") %>% 
    dplyr::select(-amb_data) %>% 
    bind_rows(
  hosp_boot_2yr_block %>% 
    unnest(tidy) %>%
    mutate(type = "Hospitalizations") %>% 
    dplyr::select(-hosp_data)
  ) %>% bind_rows(
  rme_boot_2yr_block %>% 
    unnest(tidy) %>%
    mutate(type = "Reportable Events") %>% 
    dplyr::select(-re_data)
  ) %>%
    dplyr::select(index, term:type) %>% 
    filter(term %in% "value",
          !str_detect(index, "days"),
          !str_detect(index, "may")) %>%
    mutate(index = forcats::fct_rev(dplyr::recode_factor(index, tmp_f_mean = "Temp", heat_index_mean = "HI", wbgt_f_mean = "WBGT"))) 




plot_full <-
  full_yr_df %>% 
     ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        #geom_point(aes(x = exp(statistic + bias), y = index), color = "red", shape = 4) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         facet_wrap(vars(type)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         xlab("Rate Ratio") +
         ggtitle("Full Year (Jan-Dec)")


# Heat Season

heat_season_df <-
  amb_boot_2yr_block %>% 
    unnest(tidy) %>%
    mutate(type = "Ambulatory") %>% 
    dplyr::select(-amb_data) %>% 
    bind_rows(
  hosp_boot_2yr_block %>% 
    unnest(tidy) %>%
    mutate(type = "Hospitalizations") %>% 
    dplyr::select(-hosp_data)
  ) %>% bind_rows(
  rme_boot_2yr_block %>% 
    unnest(tidy) %>%
    mutate(type = "Reportable Events") %>% 
    dplyr::select(-re_data)
  ) %>%
    dplyr::select(index, term:type) %>% 
    filter(term %in% "value",
          !str_detect(index, "days"),
           str_detect(index, "may")) %>%
    mutate(index = forcats::fct_rev(dplyr::recode_factor(index, tmp_mean_may_sep = "Temp", heat_index_mean_may_sep = "HI", wbgt_f_mean_may_sep = "WBGT")))
  
  
plot_heat <-
  heat_season_df %>% 
     ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        #geom_point(aes(x = exp(statistic + bias), y = index), color = "red", shape = 4) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         facet_wrap(vars(type)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         xlab("Rate Ratio") +
         ggtitle("Heat Season (May-Sept)") 


# Assemble plots to single figure using `patchwork`

plot_full / plot_heat

ggsave("rr_plots.png")
```


```{r plot_no_bias}

plot_full <-
  full_yr_df %>% 
     ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         facet_wrap(vars(type)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         xlab("Rate Ratio") +
         ggtitle("Full Year")


plot_heat <-
  heat_season_df %>% 
     ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         facet_wrap(vars(type)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         xlab("Rate Ratio") +
         ggtitle("Heat Season (May-Sept)") 


# Assemble plots to single figure using `patchwork`

plot_full + plot_heat
plot_full / plot_heat


```



## Bca CI plots

```{r}


# Full Year

full_yr_bca_df <-
   amb_boot_2yr_block %>% 
    unnest(tidy_bca) %>%
    mutate(type = "Out-patient") %>% 
    dplyr::select(-amb_data) %>% 
    bind_rows(
  hosp_boot_2yr_block %>% 
    unnest(tidy_bca) %>%
    mutate(type = "In-patient") %>% 
    dplyr::select(-hosp_data)
  ) %>% bind_rows(
  rme_boot_2yr_block %>% 
    unnest(tidy_bca) %>%
    mutate(type = "Reportable") %>% 
    dplyr::select(-re_data)
  ) %>%
    dplyr::select(index, term:type) %>% 
    filter(term %in% "value",
          !str_detect(index, "days"),
          !str_detect(index, "may")) %>%
    mutate(index = forcats::fct_rev(dplyr::recode_factor(index, tmp_f_mean = "Temp", heat_index_mean = "HI", wbgt_f_mean = "WBGT"))) 




plot_full_bca <-
  full_yr_bca_df %>% 
     ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_point(aes(x = exp(statistic + bias), y = index), color = "red", shape = 4) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         facet_wrap(vars(type)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         xlab("Rate Ratio") +
         ggtitle("Full Year")


# Heat Season

heat_season_bca_df <-
  amb_boot_2yr_block %>% 
    unnest(tidy_bca) %>%
    mutate(type = "Out-patient") %>% 
    dplyr::select(-amb_data) %>% 
    bind_rows(
  hosp_boot_2yr_block %>% 
    unnest(tidy_bca) %>%
    mutate(type = "In-patient") %>% 
    dplyr::select(-hosp_data)
  ) %>% bind_rows(
  rme_boot_2yr_block %>% 
    unnest(tidy_bca) %>%
    mutate(type = "Reportable") %>% 
    dplyr::select(-re_data)
  ) %>%
    dplyr::select(index, term:type) %>% 
    filter(term %in% "value",
          !str_detect(index, "days"),
           str_detect(index, "may")) %>%
    mutate(index = forcats::fct_rev(dplyr::recode_factor(index, tmp_mean_may_sep = "Temp", heat_index_mean_may_sep = "HI", wbgt_f_mean_may_sep = "WBGT")))
  
  
plot_heat_bca <-
  heat_season_bca_df %>% 
     ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_point(aes(x = exp(statistic + bias), y = index), color = "red", shape = 4) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         facet_wrap(vars(type)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         xlab("Rate Ratio") +
         ggtitle("Heat Season (May-Sept)") 


# Assemble plots to single figure using `patchwork`

plot_full_bca / plot_heat_bca

```

## Full results

```{r}
# Empirical CI

amb_boot_2yr_block %>% 
    unnest(tidy) %>%
    mutate(type = "Out-patient") %>% 
    dplyr::select(-amb_data) %>% 
    bind_rows(
  hosp_boot_2yr_block %>% 
    unnest(tidy) %>%
    mutate(type = "In-patient") %>% 
    dplyr::select(-hosp_data)
  ) %>% bind_rows(
  rme_boot_2yr_block %>% 
    unnest(tidy) %>%
    mutate(type = "Reportable") %>% 
    dplyr::select(-re_data)
  ) %>%
    dplyr::select(index, term:type) %>% 
    filter(!str_detect(index, "days")) %>%
  dplyr::select(index, type, term, statistic, conf.low, conf.high) %>% 
  group_by(index, type) %>% 
  group_split()




# Heat season, mean temp, reportable event
rme_boot_2yr_block %>% 
    unnest(tidy) %>%
    mutate(type = "Reportable") %>% 
    filter(index %in% "tmp_mean_may_sep") %>%
  dplyr::select(term, statistic, conf.low, conf.high) %>%
  mutate(term = dplyr::recode(term, installationfort_bliss   = "Fort Bliss",
                              installationfort_bragg   = "Fort Bragg",
                              installationfort_campbell   = "Fort Campbell",
                              installationfort_hood   = "Fort Hood",
                              installationfort_jackson   = "Fort Jackson",
                              installationfort_leonard_wood = "Fort Leonard Wood",
                              installationfort_polk   = "Fort Polk",
                              installationfort_riley   = "Fort Riley",
                              installationfort_stewart   = "Fort Stewart"),
         coefficient = paste0(round(statistic, 2)," ", "(", round(conf.low, 2), 
                              ", ", round(conf.high, 2), ")")) %>%
  dplyr::select(term, coefficient)

# rme, heat index, heat
rme_boot_2yr_block %>% 
    unnest(tidy) %>%
    mutate(type = "Reportable") %>% 
    filter(index %in% "heat_index_mean_may_sep") %>%
  dplyr::select(term, statistic, conf.low, conf.high) %>%
  mutate(term = dplyr::recode(term, installationfort_bliss   = "Fort Bliss",
                              installationfort_bragg   = "Fort Bragg",
                              installationfort_campbell   = "Fort Campbell",
                              installationfort_hood   = "Fort Hood",
                              installationfort_jackson   = "Fort Jackson",
                              installationfort_leonard_wood = "Fort Leonard Wood",
                              installationfort_polk   = "Fort Polk",
                              installationfort_riley   = "Fort Riley",
                              installationfort_stewart   = "Fort Stewart"),
         coefficient = paste0(round(statistic, 2)," ", "(", round(conf.low, 2), 
                              ", ", round(conf.high, 2), ")")) %>%
  dplyr::select(term, coefficient)  


# rme, wbgt, heat

rme_boot_2yr_block %>% 
    unnest(tidy) %>%
    mutate(type = "Reportable") %>% 
    filter(index %in% "wbgt_f_mean_may_sep") %>%
  dplyr::select(term, statistic, conf.low, conf.high) %>%
  mutate(term = dplyr::recode(term, installationfort_bliss   = "Fort Bliss",
                              installationfort_bragg   = "Fort Bragg",
                              installationfort_campbell   = "Fort Campbell",
                              installationfort_hood   = "Fort Hood",
                              installationfort_jackson   = "Fort Jackson",
                              installationfort_leonard_wood = "Fort Leonard Wood",
                              installationfort_polk   = "Fort Polk",
                              installationfort_riley   = "Fort Riley",
                              installationfort_stewart   = "Fort Stewart"),
         coefficient = paste0(round(statistic, 2)," ", "(", round(conf.low, 2), 
                              ", ", round(conf.high, 2), ")")) %>%
  dplyr::select(term, coefficient)  

```


```{r}
rme_boot_2yr_block %>% 
  filter(index %in% "tmp_mean_may_sep") %>% 
  unnest(re_data) %>% 
  mutate(rate = count/population) %>% 
  dplyr::rename(mean_temp = value) %>% 
  dplyr::select(installation, year, mean_temp, rate) %>% 
  mutate(installation = dplyr::recode(installation, 
                fort_benning_ga = "Fort Benning",
                fort_bliss = "Fort Bliss",
                fort_bragg = "Fort Bragg",
                fort_campbell = "Fort Campbell",
                fort_hood = "Fort Hood",
                fort_jackson = "Fort Jackson",
                fort_leonard_wood = "Fort Leonard Wood",
                fort_polk = "Fort Polk",
                fort_riley = "Fort Riley",
                fort_stewart = "Fort Stewart")) %>% 
    ggplot(aes(x = mean_temp, y = rate, color = installation, shape = installation)) +
        geom_point(size = 3) +
        geom_smooth(method = "lm", alpha = 0, size = 1.2) +
       geom_smooth(method = "lm", aes(group = 1), color = "black", se = FALSE, size = 0.5) +
        scale_shape_manual(values = 0:10) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(1)),
               axis.text.x = element_text(size = rel(1)),
               legend.position = "bottom", 
               legend.margin = margin(),
               legend.title = element_blank()) +
         guides(shape = guide_legend(nrow = 3)) +
         scale_y_continuous(limit = c(0, 0.035),oob = squish) +
         xlab("Mean temperature (May-Sept,F)") +
         ylab("HSI Reportable Event Rate \n (per 1,000/year)") 

ggsave("hsi_re_mean_tmp_summer.png")



amb_boot_2yr_block %>% 
  filter(index %in% "tmp_mean_may_sep") %>% 
  unnest(amb_data) %>% 
  mutate(rate = count/population) %>% 
  dplyr::rename(mean_temp = value) %>% 
  dplyr::select(installation, year, mean_temp, rate) %>% 
  ggplot(aes(x = mean_temp, y = rate, color = installation, shape = installation)) +
        geom_point() +
        geom_smooth(method = "lm", alpha = 0.2) +
        scale_shape_manual(values = 0:10) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75))) +
         xlab("Mean temperature (May-Sept,F)") +
         ylab("HSI Out-patient Rate (per 1,000/year)") 
```

## Outcome trends
```{r}

# By installation - outcome type
hsi_data %>% 
  filter(index %in% "tmp_f_mean") %>% 
  dplyr::select(installation, type, year, rate) %>% 
  dplyr::group_by(installation, type) %>% 
  dplyr::group_modify(~ broom::tidy(lm(rate ~ year, data = .x))) %>% 
  filter(term %in% "year")

# p < 0.05

hsi_data %>% 
  filter(index %in% "tmp_f_mean") %>% 
  dplyr::select(installation, type, year, rate) %>% 
  dplyr::group_by(installation, type) %>% 
  dplyr::group_modify(~ broom::tidy(lm(rate ~ year, data = .x))) %>% 
  filter(term %in% "year",
         p.value < 0.05)


# Overall outcome trends (combined installations)
hsi_data %>% 
  filter(index %in% "tmp_f_mean") %>% 
  dplyr::select(installation, type, year, count, population) %>%
  dplyr::group_by(type, year) %>%
  dplyr::summarise(combined_rate = sum(count) / sum(population)) %>%  dplyr::group_modify(~ broom::tidy(lm(combined_rate ~ year, data = .x))) %>% 
  filter(term %in% "year")

## Facet Combined Rate Plot

hsi_data %>% 
  filter(index %in% "tmp_f_mean") %>% 
  dplyr::select(installation, type, year, count, population) %>%
  dplyr::group_by(type, year) %>%
  dplyr::summarise(combined_rate = (sum(count) / sum(population)) * 1000) %>%
  ungroup() %>% 
  mutate(type = dplyr::recode(type,
                              `Ambulatory Data` = "Ambulatory")) %>%
  ggplot(aes(x = year, y = combined_rate)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(vars(type)) +
  ylab("Combined Rate \n (per 1,000/year)") +
  xlab(NULL) +
  theme_bw()

## Free y scales

hsi_data %>% 
  filter(index %in% "tmp_f_mean") %>% 
  dplyr::select(installation, type, year, count, population) %>%
  dplyr::group_by(type, year) %>%
  dplyr::summarise(combined_rate = (sum(count) / sum(population)) * 1000) %>%
  ungroup() %>% 
  mutate(type = dplyr::recode(type,
                              `Ambulatory Data` = "Ambulatory")) %>%
  ggplot(aes(x = year, y = combined_rate)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(vars(type), scales = "free_y") +
  ylab("Combined HSI Rate \n (per 1,000/year)") +
  xlab(NULL) +
  theme_bw()

ggsave("HSI_rates.png")
# Create new dataset for individual installations

hsi_df <-
  hsi_data %>% 
    filter(index %in% "tmp_f_mean") %>% 
    dplyr::select(installation, type, year, count, rate, population) %>% 
  mutate(type = dplyr::recode(type,
                              `Ambulatory Data` = "Ambulatory"))

hsi_data %>% 
  filter(index %in% "tmp_f_mean") %>% 
  dplyr::select(installation, type, year, count, population) %>%
  dplyr::group_by(type, year) %>%
  dplyr::summarise(combined_rate = (sum(count) / sum(population)) * 1000) %>%
  ungroup() %>% 
  mutate(type = dplyr::recode(type,
                              `Ambulatory Data` = "Ambulatory")) %>%
  ggplot(aes(x = year, y = combined_rate)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_line(data = hsi_df, aes(x = year, y = rate, group = installation), color = "gray", alpha = 0.6) +
  geom_boxplot(data = hsi_df, aes(y = rate, group = year), color = "darkgreen", alpha = 0.6) +
  facet_wrap(vars(type), scales = "free_y") +
  ylab("HSI Rate \n (per 1,000/year)") +
  xlab(NULL) +
  theme_bw()




# No facets
hsi_data %>% 
  filter(index %in% "tmp_f_mean") %>% 
  dplyr::select(installation, type, year, count, population) %>%
  dplyr::group_by(type, year) %>%
  dplyr::summarise(combined_rate = (sum(count) / sum(population)) * 1000) %>%
  ungroup() %>% 
  mutate(type = dplyr::recode(type,
                              `Ambulatory Data` = "Ambulatory")) %>%
  ggplot(aes(x = year, y = combined_rate, color = type, shape = type)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Combined Rate \n (per 1,000/year)") +
  xlab(NULL) +
  theme_bw() +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank())

## Hospitalization only

hsi_data %>% 
  filter(index %in% "tmp_f_mean",
         type %in% "Hospitalizations") %>% 
  dplyr::select(installation, type, year, count, population) %>%
  dplyr::group_by(type, year) %>%
  dplyr::summarise(combined_rate = (sum(count) / sum(population)) * 1000) %>%
  ungroup() %>% 
  mutate(type = dplyr::recode(type,
                              `Ambulatory Data` = "Ambulatory")) %>%
  ggplot(aes(x = year, y = combined_rate)) +
  geom_point() +
  geom_smooth(method = "lm", color = "#00BA3A") +
  ylab("Combined Rate \n (per 1,000/year)") +
  xlab(NULL) +
  theme_bw() +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank())

```



```{r eval = FALSE }
amb_index_2yr_fun <- function(x, i) {
  # Select random start year
  random_year <- replicate(10, sample(amb_min_yr:(amb_max_yr - 1), size = 1, replace = TRUE))
  # select the observations to subset. 
  block_obs <- 
    map_dfr(random_year, ~ x %>% 
      filter(year %in% c(random_year, random_year + 1) ))
  # run regression for given replicate, return estimated coefficients
  coefficients(MASS::glm.nb(count ~ value + installation + offset(log(population)), data = block_obs))
}



ptm <- proc.time()

amb_boot_2yr_block_full <-
  ambulatory_data_full %>% 
    nest(amb_data = installation:population) %>% 
  mutate(boot = map(amb_data, ~ boot(., amb_index_2yr_fun, 10000)),
         tidy = map(boot, ~ broom::tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "basic")))

proc.time() - ptm

write_rds(amb_boot_2yr_block_full, "data/amb_boot_2yr_block_full")
```

